% !TEX program = xelatex

\documentclass{resume}
\usepackage{comment}
\usepackage{multicol}
\usepackage{hyperref} %\hypersetup{colorlinks=false}
%\usepackage{wrapfig}
 
\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Oswin Rodrigues}
\focus{Hardware}{Embedded Software}

% {E-mail}{mobilephone}{homepage}
\contactInfo{orodrigues@uwaterloo.ca}{+1 226 606 6220}{oswinrodrigues}

\section{\faTrophy\ Goals}

\begin{itemize}[parsep=0.5ex]

  \item Micro: to excel in the design of hardware and embedded software technologies.
  
  \item Macro: to belong to a team passionate about problems that matter and solutions that revolutionize.
  
\end{itemize}

\section{\faWrench\ Tools}

\begin{itemize}[parsep=0.5ex]
  \item %Circuit:
  Schematics \& Layouts\textperiodcentered
  Soldering \& Rework\textperiodcentered
  Multimeter \& Oscilloscope\textperiodcentered
  Arduino \& Raspberry Pi
  \hfill \faBolt

  \item %Code:
  C\textperiodcentered 
  C++\textperiodcentered
  Python\textperiodcentered
  Linux\textperiodcentered
  ROS\textperiodcentered
  FPGA Programming\textperiodcentered
  MATLAB\textperiodcentered
  PLC Ladder Logic\textperiodcentered
  JavaScript%\textperiodcentered
  %Assembly\textperiodcentered
  %VHDL\textperiodcentered
  \hfill \faCode

  %\item %3D CAD Experience:
  %AutoCAD\textperiodcentered
  %Solidworks\textperiodcentered
\end{itemize}

\section{\faLineChart\ Internships}

\datedsubsection{\textbf{Hardware Engineer}}{Summer 2017}
\company{\textbf{Nuvation Energy}}{Waterloo, ON}
\textit{Fulfilling Integrated Design-to-Manufacturing (IDM) needs for released products.}
\begin{itemize}
  \item Executed Altium layout updates, team design reviews and fabbed board inspections.
  \item Investigated isoSPI bug by sniffing traffic with oscilloscope and consulting IC datasheet.
  \item Reworked boards extensively, being trained to even solder small 0402 SMT packages.
  \item Designed and built hipot test fixtures that comply with national safety regulations.
  \item Served in various other IDM-related avenues as needed, such as: building assemblies and cables, creating wiring diagrams in Visio, running in-house production tests, documenting developments in detail, facilitating environmental certification process.
\end{itemize}

\datedsubsection{\textbf{Mechatronics Engineer}}{Fall 2016}
\company{\textbf{KitchenMate Inc.}}{Toronto, ON}
\textit{Building electrical and software sub-systems in automated home-cooker.}
\begin{itemize}
  \item Designed custom linear encoder sensor with photo-interrupter pair and Python driver.
  \item Sensed heat modes on cooker with hack involving opto-isolator and ADC combination.
  \item Received abundant exposure and insight on the business side of startup operations.
  %\item Used datasheets to source parts and lab bench-top equipment to test circuit.
\end{itemize}

\datedsubsection{\textbf{AI \& Robotics Engineer}}{Winter 2016}
\company{\textbf{Kindred Systems Inc.}}{Toronto, ON}
\textit{Robot-wrangling with Python over distributed communication architecture system.}
\begin{itemize}
  \item Soldered robots' power boards and executed safety bringup.
  \item Sourced and integrated components into system with custom-coded drivers.
  \item Coded behaviour patterns of robots using Finite State Machines (FSMs) in Python.
\end{itemize}
\begin{comment}
  Informal intro to ML / N-nets, FK / IK, Grasping, FSM, DB (ES)
  People skills: pair-programming, 1-on-1, standups, blog posts, Happy Hour, AI planning, CI for internal processes, HW concept review
  Python fu: rapid prototyping / scripting AND enterprise-level code --> classes, exception-handling, logging, PDB debugging, linting, documentation
\end{comment}

\datedsubsection{\textbf{EDA \& CAD Engineer}}{Summer 2015}
\company{\textbf{Upverter Inc.}}{Toronto, ON}
\textit{Creating 150+ components' symbols and footprints; enhancing CAD features using JavaScript.}
%\textit{Enhancing PCB CAD features in hardware and software avenues.}
%\textit{Creating and verifying symbols and footprints for 150+ electronic components.}
%\begin{itemize}
  %\item Created and verified symbols and footprints for 150+ electronic components.
  %\item Used JavaScript to re-factor features and fire-fight bugs extensively.
  %\item Implemented component-tagging feature, using pin names to categorize functionality.  
%\end{itemize}
\begin{comment}
  Adjusted prioritization of design rules in layout constraint manager.
  Fixed incorrect drawing and positioning of constraint violation layout bodies.
  Re-factored event-listening logic for drawing nets in schematic editor.
  Corrected pin manager's oversight in tracking connection mappings.
  Enabled efficient BGA row enumeration during footprint generation.
\end{comment}

\datedsubsection{\textbf{Junior Mechanical Designer}}{Fall 2014}
\company{\textbf{Prodomax Automation Inc.}}{Barrie, ON}
\textit{Designing in Solidworks two stations in assembly line for vehicle's seat track mechanism.}
%\textit{Modelling in Solidworks custom jigs and fixtures for automotive part-assembly stations.}
%\begin{itemize}
  %\item Designed two stations in assembly line for vehicle's seat track mechanism. % Inserted anti-collapse spacer, stamp-pressed bushing.
  %\item Detailed and ballooned numerous tooling drawings for manufacturing.
  %\item Worked around design constraints using critical thinking and teamwork.
%\end{itemize}

\datedsubsection{\textbf{Neuro-Robotics Lab Research Assistant}}{Winter 2014}
\company{\textbf{University of Waterloo}}{Waterloo, ON}
%\textit{Setting up and operating ROS-run Turtlebot for social navigation research purposes.}
\textit{Implementing C++ and Python nodes on ROS-run Turtlebot for navigation research.}
%\begin{itemize}
  %\item Wrote C++ and Python nodes to implement navigation stack on Turtlebot. 
  %\item Published sensor, odometry and transform messages to mobile base.
  %\item Adapted existing open-source code for advanced algorithms: person-detection, SLAM navigation.
  %\item Gained immense troubleshooting experience associated with accommodating open-source software.
%\end{itemize}

\section{\faFlask\ Projects}

\datedsubsection{\href{https://guitarsandgadgets2018.wordpress.com}{\textbf{Guitar Instructor: Capstone Design Project}}}{Summer 2017 - Winter 2018}%{\faGuitar}
\begin{itemize}
  \item Built, as a team, an automated device to interactively teach chords on a guitar.
  \item Developed, personally, main controller circuit and algorithm for overall integration.
  \item Led the team with proven system integration and task co-ordination skills.
\end{itemize}

\datedsubsection{\textbf{UW Robotics Team \& Waterloo Autonomous Vehicles Lab}}{Various}%{\faCar}
\begin{itemize}
  \item Designed and reviewed schematics, layouts and components in EAGLE and DipTrace for motor shields. % on racing robot car.
  \item Spec-ed and sourced sensors for soil-analysis, given engineering and science constraints.
  \item Soldered SMT and THT parts onto bare PCBs and probed subsequently for bringup.
  %\item Researched design considerations for wireless (RF) e-stop mechanism on robot racing car.
\end{itemize}

\datedsubsection{\href{https://github.com/oswinrodrigues/LED-Matrix-And-Accelerometer}{\textbf{Tilt-Sensitive LED Matrix Panel}}}{Winter 2016}%{\faLightbulbO}
\begin{itemize}
  \item Wrote LED matrix panel driver, with two 74HC595N shift registers for I/O expansion.
  \item Wrote IMU driver for ADXL335 and MPU6050, with filter to integrate gyro and accelerometer.
\end{itemize}

%\datedsubsection{\textbf{Hackathons}}{Various}
%\begin{itemize}
  %\item \href{https://github.com/DChang87/HtN}{Pebble-run dosage notification service - \textit{SmartMeds}; used C.} \hfill Hack the North, 2015
  %\item \href{jkkd.com}{IMU-based instructor - \textit{Yoga Yoda}; developed business case. \hfill} PCH Hardware Hackathon, 2015
  %\item \href{http://devpost.com/software/drumyo}{Myo-controlled air drum kit - \textit{DruMyo}; used C++. \hfill} hackWaterloo, 2014
  %\item \href{https://github.com/fanwashere/SolidWorksControls}{Myo-enabled Solidworks controller; used Lua. \hfill} Hack the North, 2014
%\end{itemize}

%\begin{multicols}{2}

\section{\faBook\ Courses}

\datedsubsection{\textbf{Hardware}}{}
\begin{itemize}
  \item \href{http://www.ucalendar.uwaterloo.ca/1617/COURSE/course-ECE.html#ECE444}{Integrated Analog Electronics} \hfill 100\%
  \item \href{http://www.ucalendar.uwaterloo.ca/1516/COURSE/course-MTE.html#MTE220}{Sensors \& Instrumentation} \hfill 80\%
  \item \href{http://www.ucalendar.uwaterloo.ca/1516/COURSE/course-MTE.html#MTE120}{Circuits} \hfill 93\%
\end{itemize}

\datedsubsection{\textbf{Embedded Software}}{}
\begin{itemize}
  \item \href{http://www.ucalendar.uwaterloo.ca/1617/COURSE/course-ECE.html#ECE406}{Algorithm Design \& Analysis} \hfill 90\%
  \item \href{http://www.ucalendar.uwaterloo.ca/1516/COURSE/course-MTE.html#MTE341}{Microprocessor Systems \& Interfacing} \hfill 95\%
  \item \href{http://www.ucalendar.uwaterloo.ca/1516/COURSE/course-MTE.html#MTE241}{Computer Structures \& Real-Time Systems} \hfill 91\%
  \item \href{http://www.ucalendar.uwaterloo.ca/1516/COURSE/course-MTE.html#MTE262}{Data Structures \& Algorithms} \hfill 94\%
\end{itemize}

%\href{http://www.ucalendar.uwaterloo.ca/1516/COURSE/course-MTE.html#MTE320}{Actuators \& Power Electronics\hfill 92\%}

%\columnbreak

\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{Mechatronics Engineering, Honors, BASc.}}{Class of 2018}
\company{\textbf{University of Waterloo}}{Waterloo, ON}
\textit{Graduated with distinction, having a cumulative GPA of 88.23\%}

%\end{multicols}

\end{document}